Effects of the body force on the evacuation dynamics

### 2020-01-03 paper.tex
agregue el recordatorio de escribir una conclusion al final de bottleneck

The four snapshots in \ref{network_bottleneck} comfirm (visually) the fact that more rigid bodies releases the crowd environment, widening the occupied region. At $v_d=10\,$m/s (the maximum explored velocity), it can hardly be found pedestians with degree 6 when $k=1.2\,$E6, while a lot of them are present for $k$=0.

>>>>

The four snapshots in \ref{network_bottleneck} comfirm (visually) the fact that more rigid bodies releases the crowd environment, widening the occupied region. At $v_d=10\,$m/s (the maximum explored velocity), it can hardly be found pedestians with degree 6 when $k=1.2\,$E6, while a lot of them are present for $k$=0.\\

\textcolor{red}{Agregar una conclusion}
